---
title: "Bus 211 ggplot 1"
author: "Kyle Allsopp"
date: "2023-11-14"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
#enter library
library(ggplot2)
library(dplyr)
```

```{r, include=FALSE}

#enter data
data <- read.csv("/Users/kyle/Desktop/Brandeis/Bus 211/BUS 211_Output.csv")
head(data)

```

START OF VIZ


*** This section is important, run this to get the new europe_data which has the additional information we need for visualizations *** 

Subset of data
```{r}
#subset Europe data
europe_data <- data %>%
  filter(Region == "Europe & Central Asia")
head(europe_data)
```

Renaming Variables 
```{r}
europe_data <- europe_data %>%
  rename(le = Life.Expectancy, po_und = Prevalence.of.Undernourishment, co2 = CO2.Emissions, hexp = Health.Expenditure.., edu = Education.Expenditure.., comm_dis = Communicable.Diseases, non_comm_dis = Non.Communicable.Diseases, gdp_bill = GDP..Billions., acc_wtr = Access.to.clean.water)

```

Averaging Variables
```{r}
europe_data <- europe_data %>%
  group_by(Country) %>%
  mutate(
    avg_le = mean(le, na.rm = TRUE),
    avg_po_und = mean(po_und, na.rm = TRUE),
    avg_co2 = mean(co2, na.rm = TRUE),
    avg_hexp = mean(hexp, na.rm = TRUE),
    avg_edu = mean(edu, na.rm = TRUE),
    avg_comm_dis = mean(comm_dis, na.rm = TRUE),
    avg_non_comm_dis = mean(non_comm_dis, na.rm = TRUE),
    avg_gdp_bill = mean(gdp_bill, na.rm = TRUE),
    avg_acc_wtr = mean(acc_wtr, na.rm = TRUE)
  ) %>%
  ungroup()

head(europe_data)

```

More Data Cleaning / Creating East v West Variable 
```{r}
#creating a variable to define European region based on EuroVoc
europe_data <- europe_data %>%
  mutate(europe_region = case_when(
    Country %in% c("Albania", "Armenia", "Azerbaijan", "Belarus", "Bosnia and Herzegovina", "Bulgaria", "Czech Republic", "Croatia", "Georgia", "Hungary", "Moldova", "Montenegro", "North Macedonia", "Poland", "Romania", "Russia", "Serbia", "Slovakia", "Slovenia", "Ukraine") ~ "Central and Eastern Europe",
    Country %in% c("Denmark", "Estonia", "Finland", "Iceland", "Latvia", "Lithuania", "Norway", "Sweden") ~ "Northern Europe",
    Country %in% c("Cyprus", "Greece", "Holy See", "Italy", "Malta", "Portugal", "San Marino", "Spain", "Turkey") ~ "Southern Europe",
    Country %in% c("Andorra", "Austria", "Belgium", "France", "Germany", "Ireland", "Liechtenstein", "Luxembourg", "Monaco", "Netherlands", "Switzerland", "United Kingdom") ~ "Western Europe",
    TRUE ~ "Other"
  ))

#print the first few rows of the updated data
head(europe_data)

#compute which countries are in the other category, these countries are not in Europe
other_countries_list <- europe_data %>%
  filter(europe_region == "Other") %>%
  select(Country) %>%
  distinct()

print(other_countries_list)

#remove the countries we found that are not in Europe
countries_to_remove <- c("Kazakhstan", "Tajikistan", "Turkmenistan", "Uzbekistan")

europe_data <- europe_data %>%
  filter(!Country %in% countries_to_remove)

#print the updated data
head(europe_data)


#next we create a dummy variable for EU Member states, 1 for yes 0 for no
#list of EU member countries
eu_member_countries <- c(
  "Austria", "Belgium", "Bulgaria", "Croatia", "Cyprus", "Czech Republic",
  "Denmark", "Estonia", "Finland", "France", "Germany", "Greece", "Hungary",
  "Ireland", "Italy", "Latvia", "Lithuania", "Luxembourg", "Malta",
  "Netherlands", "Poland", "Portugal", "Romania", "Slovakia", "Slovenia", "Spain", "Sweden"
)

#create a new variable 'EU_member'
europe_data <- europe_data %>%
  mutate(EU_member = as.numeric(Country %in% eu_member_countries))

#print the updated data
head(europe_data)
```



## Beginning of Visuals 


# Libraries for Map of Europe
```{r}
#install.packages("ggplot2")
#install.packages("sf")
#install.packages("rnaturalearth")
#install.packages("rnaturalearthdata")
```


# Average Life Expectancy Europe Map 
```{r}
library(ggplot2)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)

# Load geographical data for European countries
european_countries <- ne_countries(scale = "medium", continent = "europe", returnclass = "sf")

# Merge your data with geographical data (ensure the country names match)
merged_data <- merge(european_countries, europe_data, by.x = "name", by.y = "Country")

# Create the map
ggplot(data = merged_data) +
  geom_sf(aes(fill = avg_le), color = "black", size = 0.5) + # Adjust the size for better border visibility
  scale_fill_gradientn(colors = c("red", "yellow", "green"), na.value = "grey50") + # Color palette from red to green, grey for missing data
  labs(title = "Average Life Expectancy in Europe",
       subtitle = "Life expectancy by country, colored from lower (red) to higher (green)",
       caption = "Source: Your Data Source",
       fill = "Life Expectancy") +
  theme_minimal() +
  theme(legend.position = "right") + # Adjust legend position if needed
  coord_sf(crs = st_crs(4326), xlim = c(-10, 40), ylim = c(35, 70)) # Adjust map limits if needed

# Print the map
#print(ggplot_map)

```

# Map of EU Member States in Europe 
```{r}

library(ggplot2)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)

# Load geographical data for European countries
european_countries <- ne_countries(scale = "medium", continent = "europe", returnclass = "sf")

# Merge your data with geographical data (ensure the country names match)
merged_data <- merge(european_countries, europe_data, by.x = "name", by.y = "Country")

# Create the map with EU member states highlighted
eu_map <- ggplot(data = merged_data) +
  geom_sf(aes(fill = as.factor(EU_member)), color = "black", size = 0.5) +
  scale_fill_manual(values = c("0" = "grey", "1" = "blue"), 
                    labels = c("Non-EU Member", "EU Member"),
                    name = "Membership") +
  labs(title = "EU Member States in Europe",
       subtitle = "EU Member States are highlighted in blue") +
  theme_minimal() +
  theme(legend.position = "right") +
  coord_sf(crs = st_crs(4326), xlim = c(-10, 40), ylim = c(35, 70))

# Print the map
print(eu_map)


```

# Multivariate Regression 
```{r}

# Load necessary libraries
library(dplyr)
library(car)

# Assuming your data frame is named europe_data and it's already been cleaned and prepared
# We will run a linear model (multivariate regression) with life expectancy (le) as the dependent variable

# Multivariate Linear Regression
lifeExp_model <- lm(le ~ gdp_bill + hexp + edu + co2 + po_und + comm_dis + non_comm_dis + acc_wtr, data = europe_data)

# Summary of the model to view coefficients and statistics
summary(lifeExp_model)

# Checking for multicollinearity with Variance Inflation Factor (VIF)
vif(lifeExp_model)  # Values > 5 or 10 indicate high multicollinearity

# Residual checks for assumptions of linear regression
par(mfrow=c(2,2))
plot(lifeExp_model)


```
Top variables are Gdp, po_und, comm_dis, acc_wtr, hexp 

# Comparative Analysis by Region 
```{r}

ggplot(europe_data, aes(x = europe_region, y = avg_le)) +
  geom_boxplot() +
  labs(title = "Life Expectancy Across European Regions", x = "Region", y = "Average Life Expectancy")

```

# Adding Europe data 2 for population and diseases 
```{r}

#input new data from Tableau prep that included population
europe_data2 <- read.csv("/Users/kyle/Desktop/Brandeis/Bus 211/europe_data2.csv")


#replace the existing europe_data with the new data
europe_data <- europe_data2


europe_data <- europe_data %>%
  group_by(Country) %>%
  mutate(avg_population = mean(population, na.rm = TRUE))

#communicable
europe_data <- europe_data %>%
  mutate(avg_cd_per_capita = avg_comm_dis / avg_population)


#noncommunicable
europe_data <- europe_data %>%
  mutate(avg_ncd_per_capita = avg_non_comm_dis / avg_population)

```

# Maps of Average of Predictor Variables 
```{r}

# Load required libraries
library(ggplot2)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)

# Load geographical data for European countries
european_countries <- ne_countries(scale = "medium", continent = "europe", returnclass = "sf")

# Merge your data with geographical data (ensure the country names match)
merged_data <- merge(european_countries, europe_data, by.x = "name", by.y = "Country")

# Function to create a map based on a given variable
create_map <- function(variable, title, low_color, high_color) {
  ggplot(data = merged_data) +
    geom_sf(aes(fill = get(variable)), color = "black", size = 0.5) + 
    scale_fill_gradientn(colors = c(low_color, high_color), na.value = "grey50") + 
    labs(title = title,
         fill = variable) +
    theme_minimal() +
    theme(legend.position = "right") + 
    coord_sf(crs = st_crs(4326), xlim = c(-10, 40), ylim = c(35, 70))
}

# Map for Access to Clean Water
create_map("avg_acc_wtr", "Average Access to Clean Water in Europe", "blue", "green")

# Map for Prevalence of Undernourishment
create_map("avg_po_und", "Average Prevalence of Undernourishment in Europe", "orange", "red")

# Map for Communicable Diseases
create_map("avg_comm_dis", "Average Communicable Diseases in Europe", "purple", "pink")

# Execute these functions to create the maps
map_acc_wtr <- create_map("avg_acc_wtr", "Average Access to Clean Water in Europe", "blue", "green")
map_po_und <- create_map("avg_po_und", "Average Prevalence of Undernourishment in Europe", "orange", "red")
map_comm_dis <- create_map("avg_comm_dis", "Average Communicable Diseases in Europe", "purple", "pink")

# Map for Education Expenditure
map_edu <- create_map("avg_edu", "Average Education Expenditure in Europe", "#fee5d9", "#a50f15")

# Map for Health Expenditure
map_hexp <- create_map("avg_hexp", "Average Health Expenditure in Europe", "#f7f7f7", "#652526")

# Map for GDP in Billions
map_gdp <- create_map("avg_gdp_bill", "Average GDP in Billions in Europe", "#ffffcc", "#1a9641")

# Print the maps
print(map_acc_wtr)
print(map_po_und)
print(map_comm_dis)
print(map_edu)
print(map_hexp)
print(map_gdp)


```

# Map of Communicable Diseases Per Capita for Europe 
```{r}
# Assuming 'merged_data' is already created and contains the necessary variables

# Function to create a map based on a given variable
create_map <- function(variable, title, low_color, high_color) {
  ggplot(data = merged_data) +
    geom_sf(aes(fill = get(variable)), color = "black", size = 0.5) + 
    scale_fill_gradientn(colors = c(low_color, high_color), na.value = "grey50") + 
    labs(title = title,
         fill = variable) +
    theme_minimal() +
    theme(legend.position = "right") + 
    coord_sf(crs = st_crs(4326), xlim = c(-10, 40), ylim = c(35, 70))
}

# Let's choose a teal color gradient for communicable diseases per capita
map_cd_per_capita <- create_map("avg_cd_per_capita", "Communicable Diseases per Capita in Europe", "#a2d4ec", "#004c6d")

# Print the communicable diseases per capita map
print(map_cd_per_capita)


```

# Map of EU and non EU Members 
```{r eu-members-map}

# Assuming merged_data already contains the 'EU_member' column with 1 for EU members and 0 for non-members

# Create the map highlighting EU member states with blue and non-members with grey
ggplot(data = merged_data) +
  geom_sf(aes(fill = as.factor(EU_member)), color = "black", size = 0.5) +
  scale_fill_manual(values = c("0" = "grey", "1" = "blue"), name = "EU Membership",
                    labels = c("Non-EU Member", "EU Member")) +
  labs(title = "EU and Non-EU Countries in Europe",
       subtitle = "EU member states in blue, non-members in grey") +
  theme_minimal() +
  theme(legend.position = "right") +
  coord_sf(crs = st_crs(4326), xlim = c(-10, 40), ylim = c(35, 70))

# Print the map
#ggplot_map

```

# Map of Average Life Expectancy for EU Countries 
```{r}
library(ggplot2)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)

# Assuming europe_data already contains the 'EU_member' column with 1 for EU members and 0 for non-members

# Load geographical data for European countries
european_countries <- ne_countries(scale = "medium", continent = "europe", returnclass = "sf")

# Merge your data with geographical data (ensure the country names match)
merged_data <- merge(european_countries, europe_data, by.x = "name", by.y = "Country")

# Create the map showing only EU countries with life expectancy
ggplot(data = merged_data) +
  geom_sf(aes(fill = ifelse(EU_member == 1, avg_le, NA)), color = "black", size = 0.5) +
  scale_fill_gradientn(colors = c("red", "yellow", "green"), na.value = "grey50", 
                       limits = c(min(merged_data$avg_le, na.rm = TRUE), max(merged_data$avg_le, na.rm = TRUE)),
                       name = "Life Expectancy") +
  labs(title = "Average Life Expectancy in EU Countries",
       subtitle = "EU countries colored by life expectancy, non-EU countries in grey") +
  theme_minimal() +
  theme(legend.position = "right") +
  coord_sf(crs = st_crs(4326), xlim = c(-10, 40), ylim = c(35, 70))

# Print the map
#ggplot_map

```

# Map of EU Member States in Europe 
```{r}

library(ggplot2)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)

# Load geographical data for European countries
european_countries <- ne_countries(scale = "medium", continent = "europe", returnclass = "sf")

# Merge your data with geographical data (ensure the country names match)
merged_data <- merge(european_countries, europe_data, by.x = "name", by.y = "Country")

# Create the map highlighting EU member states
ggplot(data = merged_data) +
  geom_sf(aes(fill = ifelse(EU_member == 1, "EU Member", "Non-EU Member")), color = "black", size = 0.5) +
  scale_fill_manual(values = c("Non-EU Member" = "grey", "EU Member" = "blue"),
                    name = "Membership") +
  labs(title = "EU Member States in Europe",
       subtitle = "Countries with EU membership are highlighted") +
  theme_minimal() +
  theme(legend.position = "right") +
  coord_sf(crs = st_crs(4326), xlim = c(-10, 40), ylim = c(35, 70))

# Print the map
print(eu_map)


```

# Map of four European Regions 
```{r}

library(ggplot2)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)

# Load geographical data for European countries
european_countries <- ne_countries(scale = "medium", continent = "europe", returnclass = "sf")

# Merge your data with geographical data (ensure the country names match)
merged_data <- merge(european_countries, europe_data, by.x = "name", by.y = "Country")

# Create the map highlighting the four European regions
eu_region_map <- ggplot(data = merged_data) +
  geom_sf(aes(fill = europe_region), color = "black", size = 0.5) +
  scale_fill_manual(values = c("Central and Eastern Europe" = "#1b9e77",
                               "Northern Europe" = "#d95f02",
                               "Southern Europe" = "#7570b3",
                               "Western Europe" = "#e7298a"),
                    name = "Region") +
  labs(title = "European Regions",
       subtitle = "Each color represents a different region") +
  theme_minimal() +
  theme(legend.position = "right") +
  coord_sf(crs = st_crs(4326), xlim = c(-10, 40), ylim = c(35, 70))

# Print the map
print(eu_region_map)

```

# LE and Education Exp in Europe, LE and Access to Clean Water in Europe, LE and Prev of Und in Europe 
```{r}

# Plotting Life Expectancy with Access to Clean Water based on Regions
ggplot(europe_data, aes(x = avg_acc_wtr, y = avg_le, group = europe_region, color = europe_region)) +
  geom_line() +
  geom_point() +
  labs(title = "Life Expectancy with Access to Clean Water in Europe",
       x = "Average Access to Clean Water",
       y = "Average Life Expectancy") +
  theme_minimal() +
  scale_color_manual(values = c("Central and Eastern Europe" = "red",
                                "Northern Europe" = "blue",
                                "Southern Europe" = "green",
                                "Western Europe" = "purple",
                                "Other" = "gray")) 

# Plotting Life Expectancy against Education Expenditure with Country Labels
ggplot(europe_data, aes(x = avg_edu, y = avg_le)) +
  geom_point(aes(color = europe_region), size = 3) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  geom_text(aes(label = Country), nudge_x = 0.2, nudge_y = 0.2, size = 2.5, check_overlap = TRUE) +
  labs(title = "Life Expectancy and Education Expenditure in Europe",
       x = "Average Education Expenditure",
       y = "Average Life Expectancy") +
  theme_minimal() +
  scale_color_manual(values = c("Central and Eastern Europe" = "red",
                                "Northern Europe" = "blue",
                                "Southern Europe" = "green",
                                "Western Europe" = "purple",
                                "Other" = "gray"))


# Jitter Plot for Average Life Expectancy and Average Prevalence of Undernourishment
ggplot(europe_data, aes(x = avg_po_und, y = avg_le)) +
  geom_jitter(aes(color = europe_region), width = 0.2, height = 0.2, alpha = 0.7) +
  geom_text(aes(label = Country), nudge_x = 0.1, nudge_y = 0.1, size = 2.5, check_overlap = TRUE) +
  labs(title = "Life Expectancy and Prevalence of Undernourishment in Europe",
       x = "Average Prevalence of Undernourishment (log scale)",
       y = "Average Life Expectancy") +
  theme_minimal() +
  scale_color_manual(values = c("Central and Eastern Europe" = "red",
                                "Northern Europe" = "blue",
                                "Southern Europe" = "green",
                                "Western Europe" = "purple",
                                "Other" = "gray")) +
  scale_x_log10()  # Apply log scale to the x-axis



```

Diverging Plot
```{r}
ggplot(europe_data, aes(x = reorder(Country, avg_le), y = avg_le, label = avg_le)) +
  geom_bar(stat = 'identity', aes(fill = ifelse(avg_le > median(europe_data$avg_le, na.rm = TRUE), "above", "below")), width = 0.5) +
  scale_fill_manual(name = "Average Life Expectancy", 
                    labels = c("Above Median", "Below Median"), 
                    values = c("above" = "#00ba38", "below" = "#f8766d")) +
  labs(subtitle = "Average Variables in Europe & Central Asia", 
       title = "Diverging Bars") +
  coord_flip()
```
```{r}
overall_median_le <- median(europe_data$Life.Expectancy, na.rm = TRUE)

europe_data <- europe_data %>%
  group_by(Country) %>%
  summarize(avg_le = mean(le, na.rm = TRUE))

# Bar plot for average life expectancy by country

```



```{r}
#write europe data to a csv
write.csv(europe_data, "europe_data.csv", row.names = FALSE)

#input new data from Tableau prep that included population
europe_data2 <- read.csv("/Users/kyle/Desktop/Brandeis/Bus 211/europe_data2.csv")

#replace the existing europe_data with the new data
europe_data <- europe_data2

#create average population
europe_data <- europe_data %>%
  group_by(Country) %>%
  mutate(avg_population = mean(population, na.rm = TRUE))

#create avg communicable diseases per capita
europe_data <- europe_data %>%
  mutate(avg_cd_per_capita = avg_comm_dis / avg_population)

#create avg non communicable diseases per capita
europe_data <- europe_data %>%
  mutate(avg_ncd_per_capita = avg_non_comm_dis / avg_population)


```



```{r}
# Calculate the weighted average access to clean water
europe_data <- europe_data %>%
  mutate(weighted_avg_acc_wtr = sum(avg_acc_wtr * avg_population, na.rm = TRUE) / sum(avg_population, na.rm = TRUE))

# Bar plot for weighted average access to clean water by region
ggplot(europe_data, aes(x = reorder(europe_region, -weighted_avg_acc_wtr), y = weighted_avg_acc_wtr)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  labs(title = "Weighted Average Access to Clean Water Across European Regions",
       x = "European Region",
       y = "Weighted Average Access to Clean Water") +
  theme_minimal()

```

```{r}
ggplot(europe_data, aes(x = europe_region, y = avg_population, fill = europe_region)) +
  geom_bar(stat = "identity") +
  labs(title = "Average Population Across European Regions",
       x = "European Region",
       y = "Average Population") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r}
ggplot(europe_data, aes(x = reorder(Country, avg_population), y = avg_population, fill = europe_region)) +
  geom_bar(stat = "identity") +
  labs(title = "Average Population Across European Countries",
       x = "Country",
       y = "Average Population") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
ggplot(europe_data, aes(x = reorder(Country, avg_le), y = avg_le, fill = europe_region)) +
  geom_bar(stat = "identity") +
  labs(title = "Average Life Expectancy Across European Countries",
       x = "Country",
       y = "Average Life Expectancy") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

Communicable diseases per capita 
```{r}
ggplot(europe_data, aes(x = avg_cd_per_capita, y = avg_le, color = europe_region)) +
  geom_point(size = 3) +
  labs(subtitle = "Average Life Expectancy vs. Communicable Diseases per Capita",
       title = "Scatter Plot") +
  scale_color_manual(name = "Region",
                     values = c("Northern Europe" = "blue", "Central and Eastern Europe" = "red", "Southern Europe" = "green", "Western Europe" = "purple", "Other" = "#BDBDBD")) +
  theme_minimal()
```

Communicable diseases by country
```{r}
ggplot(europe_data, aes(x = reorder(Country, -avg_cd_per_capita), y = avg_cd_per_capita, fill = europe_region)) +
  geom_bar(stat = "identity", width = 0.8) +
  labs(subtitle = "Communicable Diseases per Capita by Country",
       title = "Bar Plot",
       x = "Country",
       y = "Communicable Diseases per Capita") +
  scale_fill_manual(name = "Region",
                     values = c("Northern Europe" = "blue", "Central and Eastern Europe" = "red", "Southern Europe" = "green", "Western Europe" = "purple", "Other" = "#BDBDBD")) +
  theme_minimal() +
  theme(legend.position = c(0.8, 0.8)) + 
  coord_flip()
```


```{r}
average_le <- europe_data %>%
  group_by(Country, europe_region) %>%
  summarize(avg_le = mean(le, na.rm = TRUE))


ggplot(average_le, aes(x = reorder(Country, -avg_le), y = avg_le, fill = europe_region)) +
  geom_bar(stat = "identity", width = 0.8) +
  labs(subtitle = "Average Life Expectancy by Country",
       title = "Bar Plot") +
  scale_fill_manual(name = "Region",
                    values = c("Northern Europe" = "blue", "Central and Eastern Europe" = "red", "Southern Europe" = "green", "Western Europe" = "purple", "Other" = "#BDBDBD")) +
  theme_minimal() +
  theme(legend.position = "bottom") +
  coord_flip() +
  xlab("Country") +
  ylab("Average Life Expectancy")

```



Education Expenditure 
```{r}
ggplot(europe_data, aes(x = avg_hexp, y = le, color = europe_region)) +
  geom_point(size = 2) +  # Adjust the size of the points
  geom_smooth(method = "lm", se = FALSE, color = "black") +  # Add a linear trend line
  labs(subtitle = "Life Expectancy vs. Health Expenditure per Capita",
       title = "Scatter Plot with Trend Line") +
  scale_color_manual(name = "Region",
                     values = c("Northern Europe" = "#00ba38", "Central and Eastern Europe" = "red", "Southern Europe" = "skyblue", "Western Europe" = "purple", "Other" = "#BDBDBD")) +
  theme_minimal() +
  xlab("Health Expenditure per Capita") +  
  ylab("Life Expectancy")
```


```{r}
ggplot(europe_data, aes(x = reorder(Country, avg_hexp), y = avg_hexp, fill = europe_region)) +
  geom_bar(stat = "identity", width = 0.8) +
  labs(subtitle = "Health Expenditure per Capita by Country",
       title = "Bar Plot",
       x = "Country",
       y = "Health Expenditure per Capita") +
  scale_fill_manual(name = "Region",
                     values = c("Northern Europe" = "#00ba38", "Central and Eastern Europe" = "red", "Southern Europe" = "skyblue", "Western Europe" = "purple", "Other" = "#BDBDBD")) +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.justification = "right") +
  coord_flip()
```





