---
title: "LE_GLobal_final version"
author: "Kyle, Salman, Sana, Erick and Maria"
date: "2023-10-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Initial Setup and creating some new columns 
```{r}

# Load the libraries into R studio  
library(tidyverse)
library(dplyr)
library(ggplot2)
library(plotly)
library(ggpubr)

# Load the data into R from the output csv file 
# Edit path here
data <- read.csv("/Users/salmanhaider_2020/Desktop/Info Viz Report 3/240_Output(2).csv")

# Create GDP per capita column and columns for a few other variables in the data 
data <- data %>%
  mutate(
    GDPperCapita = (((GDP..Billions.)*1000000000)/Population..historical.estimates.),
    CO2EmissionsperCapita = CO2.Emissions/Population..historical.estimates.,
InjuriesperCapita = Injuries/Population..historical.estimates.,
  CommunicableperCapita = Communicable.Diseases/Population..historical.estimates.,
  NonCommunicableperCapita = Non.Communicable.Diseases/Population..historical.estimates.)

# Define the desired order of levels for the Income.Group factor
income_levels <- c("High income", "Upper middle income", "Lower middle income", "Low income")

# Reorder the levels of the Income.Group factor
data$Income.Group <- factor(data$Income.Group, levels = income_levels)

# Load the names of the columns
names(data)

# Preview the first few rows to ensure it's loaded correctly
head(data)

# Check for missing values in each column
missing_values <- colSums(is.na(data))

# Print the count of missing values per column
print(missing_values)

# Print each column name on a new line

column_names <- names(data)
for(name in column_names) {
  cat(name, "\n")
}


```

Boxplots
```{r}

# Load the libraries into R studio  
library(tidyverse)
library(dplyr)
library(ggplot2)
library(plotly)
library(ggpubr)

# Load the data into R from the output csv file 
# Edit path here
data <- read.csv("/Users/salmanhaider_2020/Desktop/Info Viz Report 3/240_Output(2).csv")

# Calculate the number of null values for each column
null_count <- sapply(data, function(x) sum(is.na(x)))

# Display the results
print(null_count)

# Create additional columns
data <- data %>%
  mutate(
    GDPperCapita = (((GDP..Billions.)*1000000000)/Population..historical.estimates.),
    CO2EmissionsperCapita = CO2.Emissions/Population..historical.estimates.,
    InjuriesperCapita = Injuries/Population..historical.estimates.,
    CommunicableperCapita = Communicable.Diseases/Population..historical.estimates.,
    NonCommunicableperCapita = Non.Communicable.Diseases/Population..historical.estimates.)


################################################
#### LIFE EXPECTANCY
# Define your dataset and column name
#data <- my_data
column_name <- "Life.Expectancy"

# Specify the columns you want to keep
columns_to_keep <- c("Country", "Region", "Income.Group", "Life.Expectancy")

# Subset dataset to keep selected columns
subset_data <- data[, columns_to_keep]

# Calculate the IQR for the specified column
Q1 <- quantile(data[[column_name]], 0.25)
Q3 <- quantile(data[[column_name]], 0.75)
IQR_value <- Q3 - Q1

# Set a threshold to determine outliers (you can adjust this threshold)
threshold <- 1.5

# Identify outliers
outliers <- subset_data %>%
  filter(subset_data[[column_name]] < Q1 - threshold * IQR_value | subset_data[[column_name]] > Q3 + threshold * IQR_value)

# Exclude outliers from the dataset
filtered_data <- subset_data %>%
  filter(!(subset_data[[column_name]] %in% outliers[[column_name]]))

# BOXPLOTS FOR LIFE EXPECTANCY
# create boxplot with Outliers
ggplot(data, aes(Life.Expectancy, Income.Group, fill = Income.Group)) +
  geom_boxplot(notch=TRUE, show.legend = FALSE) +
  ggtitle("Life Expectancy by Income Group") +
  ylab("Income Group") +
  xlab("Life Expectancy")

# create boxplot without Outliers
ggplot(filtered_data, aes(Life.Expectancy, Income.Group, fill = Income.Group)) +
  geom_boxplot(notch=TRUE, show.legend = FALSE, outlier.shape = NA) +
  ggtitle("Life Expectancy by Income Group") +
  ylab("Income Group") +
  xlab("Life Expectancy")

# Summary of unfiltered and filtered data
summary(data)
summary(filtered_data)

#########################

#### ACCESS TO CLEAN WATER
# Define your dataset and column name
#data <- my_data
column_name <- "Access.to.clean.water"

# Specify the columns you want to keep
columns_to_keep <- c("Country", "Region", "Income.Group", "Access.to.clean.water")

# Subset dataset to keep selected columns
subset_data <- data[, columns_to_keep]

# Calculate the IQR for the specified column
Q1 <- quantile(data[[column_name]], 0.25, na.rm = TRUE)
Q3 <- quantile(data[[column_name]], 0.75, na.rm = TRUE)
IQR_value <- Q3 - Q1

# Set a threshold to determine outliers (you can adjust this threshold)
threshold <- 1.5

# Identify outliers
outliers <- subset_data %>%
  filter(subset_data[[column_name]] < Q1 - threshold * IQR_value | subset_data[[column_name]] > Q3 + threshold * IQR_value)

# Exclude outliers from the dataset
filtered_data <- subset_data %>%
  filter(!(subset_data[[column_name]] %in% outliers[[column_name]]))

# BOXPLOTS FOR LIFE EXPECTANCY
# create boxplot with Outliers
ggplot(data, aes(Access.to.clean.water, Income.Group, fill = Income.Group)) +
  geom_boxplot(notch=TRUE, show.legend = FALSE) +
  ggtitle("Access to Clean Water % by Income Group") +
  ylab("Income Group") +
  xlab("Access to Clean Water %")

# create boxplot without Outliers
ggplot(filtered_data, aes(Access.to.clean.water, Income.Group, fill = Income.Group)) +
  geom_boxplot(notch=TRUE, show.legend = FALSE, outlier.shape = NA) +
  ggtitle("Access to Clean Water % by Income Group") +
  ylab("Income Group") +
  xlab("Access to Clean Water %")

# Summary of unfiltered and filtered data
summary(data)
summary(filtered_data)



```

Cluster Analysis (1)
```{r}
# Create dataframe with averages by country
avg_data_by_country <- data %>%
  group_by(Country) %>%
  summarise_all(.funs = list(mean), na.rm = TRUE)

avg_data_by_country <- avg_data_by_country %>%
  select(-Year)

unique_pairs <- data %>%
  distinct(Country, Region, Income.Group)

avg_data_by_country <- avg_data_by_country %>%
  left_join(unique_pairs, by = "Country")

avg_data_by_country <- avg_data_by_country %>%
  select(-Region.x, -Income.Group.x) %>%
  rename(
    Region = Region.y,
    Income.Group = Income.Group.y
  )

# Define the desired order of levels for the Income.Group factor
income_levels <- c("High income", "Upper middle income", "Lower middle income", "Low income")

# Reorder the levels of the Income.Group factor
avg_data_by_country$Income.Group <- factor(avg_data_by_country$Income.Group, levels = income_levels)
```
Cluster Analysis (2)
```{r}
library(stats)

# Life Expectancy and Health Expenditure %
# Visualizing LE and Health
ggplot(avg_data_by_country, aes(x = `Health.Expenditure..`, y = `Life.Expectancy`, color = `Income.Group`)) +
  geom_point() +
  ggtitle("Avg Life Expectancy vs Avg Health Expenditure") +
  xlab("Health Expenditure % of GDP") + ylab("Life Expectancy")

# Normalization
avg_data_by_country_scaled <- data.frame(avg_data_by_country)

avg_data_by_country_scaled[, c("Life.Expectancy_scaled", "Health.Expenditure_scaled")] =  scale(avg_data_by_country[, c("Life.Expectancy", "Health.Expenditure..")])

# Fitting and evaluating the model
# Get two columns of interest
LE_health <- avg_data_by_country_scaled[, c("Country", "Life.Expectancy", "Health.Expenditure..", "Life.Expectancy_scaled", "Health.Expenditure_scaled", "Region", "Income.Group")]

LE_health <- na.omit(LE_health)

# how many clusters
n_clusters <- 10
# initialize within sum of squares error
wss <- numeric(n_clusters)

# Set seed
set.seed(123)

for (i in 1:n_clusters) {
  # fit model
  km_LE_health.out <- kmeans(LE_health[, c("Life.Expectancy_scaled", "Health.Expenditure_scaled")], centers = i)
  # save wss
  wss[i] <- km_LE_health.out$tot.withinss
}

# create scree plot
wss_df <- tibble(clusters = 1:n_clusters, wss = wss)

scree_plot <- ggplot(wss_df, aes(x = clusters, y = wss, group = 1)) +
  geom_point() +
  geom_line() +
  scale_x_continuous(breaks = c(2, 4, 6, 8, 10)) +
  xlab('Number of clusters') +
  ylab('wss')

scree_plot

km_LE_health.out <- kmeans(LE_health[, c("Life.Expectancy_scaled", "Health.Expenditure_scaled")], centers = 4)
km_LE_health.out

# Plot results
LE_health$cluster_id <- factor(km_LE_health.out$cluster)
ggplot(LE_health, aes(`Health.Expenditure..`, `Life.Expectancy`, color = cluster_id, label = `Country`, shape = `Income.Group`)) +
    geom_point(alpha = 0.5) +
    #geom_text(size = 3) +
    xlab("Health Expenditure %") +
    ylab("Life Expectancy")

LE_health$cluster_id <- factor(km_LE_health.out$cluster)
ggplot(LE_health, aes(`Health.Expenditure..`, `Life.Expectancy`, color = cluster_id, label = `Country`)) +
    geom_point(alpha = 0.5) +
    geom_text(size = 3) +
  ggtitle("Cluster Analysis of Life Expectancy and Health Expenditures") +
    xlab("Health Expenditure %") +
    ylab("Life Expectancy")

```
Cluster Analysis (3)
```{r}

# Life Expectancy and Undernourishment
# Visualizing LE and Health
ggplot(avg_data_by_country, aes(x = `Prevalence.of.Undernourishment`, y = `Life.Expectancy`, color = `Income.Group`)) +
  geom_point() +
  ggtitle("Avg Life Expectancy vs Avg Undernourishment") +
  xlab("Avg Prevalence of Undernourishment") + ylab("Life Expectancy")

# Normalization
avg_data_by_country_scaled2 <- data.frame(avg_data_by_country)

avg_data_by_country_scaled2[, c("Life.Expectancy_scaled", "Prevalence.of.Undernourishment_scaled")] =  scale(avg_data_by_country[, c("Life.Expectancy", "Prevalence.of.Undernourishment")])

# Fitting and evaluating the model
# Get two columns of interest
LE_undernourishment <- avg_data_by_country_scaled2[, c("Country", "Life.Expectancy", "Prevalence.of.Undernourishment", "Life.Expectancy_scaled", "Prevalence.of.Undernourishment_scaled", "Region", "Income.Group")]

LE_undernourishment <- na.omit(LE_undernourishment)

# how many clusters
n_clusters <- 10

# initialize within sum of squares error
wss <- numeric(n_clusters)

# Set seed
set.seed(123)

for (i in 1:n_clusters) {
  # fit model
  km_LE_undernourishment.out <- kmeans(LE_undernourishment[, c("Life.Expectancy_scaled", "Prevalence.of.Undernourishment_scaled")], centers = i)
  
  # save wss
  wss[i] <- km_LE_undernourishment.out$tot.withinss
}

# create scree plot
wss_df <- tibble(clusters = 1:n_clusters, wss = wss)

scree_plot <- ggplot(wss_df, aes(x = clusters, y = wss, group = 1)) +
  geom_point() +
  geom_line() +
  scale_x_continuous(breaks = c(2, 4, 6, 8, 10)) +
  xlab('Number of clusters') +
  ylab('wss')

scree_plot

km_LE_undernourishment.out <- kmeans(LE_undernourishment[, c("Life.Expectancy_scaled", "Prevalence.of.Undernourishment_scaled")], centers = 4)
km_LE_undernourishment.out

# Plot results
LE_undernourishment$cluster_id <- factor(km_LE_undernourishment.out$cluster)
ggplot(LE_undernourishment, aes(`Prevalence.of.Undernourishment`, `Life.Expectancy`, color = cluster_id, label = `Country`, shape = `Income.Group`)) +
    geom_point(alpha = 0.8) +
    #geom_text(size = 3) +
  ggtitle("Cluster Analysis of Life Expectancy and Prevalence of Undernourishment") +
    xlab("Prevalence of Undernourishment") +
    ylab("Life Expectancy") +
    scale_y_log10() + scale_x_log10()

```
Cluster Analysis (4)
```{r}

# Life Expectancy and GDP per capita
# Visualizing LE and GDP
ggplot(avg_data_by_country, aes(x = `GDPperCapita`, y = `Life.Expectancy`, color = `Income.Group`)) +
  geom_point() +
  ggtitle("Avg Life Expectancy vs Avg GDP per Capita") +
  xlab("Avg GDP per Capita") + ylab("Life Expectancy")

# Normalization
avg_data_by_country_scaled3 <- data.frame(avg_data_by_country)

avg_data_by_country_scaled3[, c("Life.Expectancy_scaled", "GDPperCapita_scaled")] =  scale(avg_data_by_country[, c("Life.Expectancy", "GDPperCapita")])

# Fitting and evaluating the model
# Get two columns of interest
LE_GDP <- avg_data_by_country_scaled3[, c("Country", "Life.Expectancy", "GDPperCapita", "Life.Expectancy_scaled", "GDPperCapita_scaled", "Region", "Income.Group")]

LE_GDP <- na.omit(LE_GDP)

# how many clusters
n_clusters <- 10

# initialize within sum of squares error
wss <- numeric(n_clusters)

# Set seed
set.seed(123)

for (i in 1:n_clusters) {
  # fit model
  km_LE_GDP.out <- kmeans(LE_GDP[, c("Life.Expectancy_scaled", "GDPperCapita_scaled")], centers = i)
  
  # save wss
  wss[i] <- km_LE_GDP.out$tot.withinss
}

# create scree plot
wss_df <- tibble(clusters = 1:n_clusters, wss = wss)

scree_plot <- ggplot(wss_df, aes(x = clusters, y = wss, group = 1)) +
  geom_point() +
  geom_line() +
  scale_x_continuous(breaks = c(2, 4, 6, 8, 10)) +
  ggtitle("Line plot of WSS vs Number of Clusters") +
  xlab('Number of clusters') +
  ylab('wss')

scree_plot

km_LE_GDP.out <- kmeans(LE_GDP[, c("Life.Expectancy_scaled", "GDPperCapita_scaled")], centers = 3)
km_LE_GDP.out

# Plot results
LE_GDP$cluster_id <- factor(km_LE_GDP.out$cluster)
ggplot(LE_GDP, aes(`GDPperCapita`, `Life.Expectancy`, color = cluster_id, label = `Country`, shape = `Income.Group`)) +
    geom_point(alpha = 0.5) +
    #geom_text(size = 3) +
  ggtitle("Cluster Analysis of Life Expectancy and GDP per Capita") +
    xlab("GDP per Capita (log10)") +
    ylab("Life Expectancy") +
    scale_x_log10()

```
Cluster Analysis (5)
```{r}
# Life Expectancy and Unemployment
# Visualizing LE and Unemployment
ggplot(avg_data_by_country, aes(x = `Unemployment`, y = `Life.Expectancy`, color = `Income.Group`)) +
  geom_point() +
  ggtitle("Avg Life Expectancy vs Avg Unemployment") +
  xlab("Avg Unemployment") + ylab("Life Expectancy")

# Normalization
avg_data_by_country_scaled4 <- data.frame(avg_data_by_country)

avg_data_by_country_scaled4[, c("Life.Expectancy_scaled", "Unemployment_scaled")] =  scale(avg_data_by_country[, c("Life.Expectancy", "Unemployment")])

# Fitting and evaluating the model
# Get two columns of interest
LE_ump <- avg_data_by_country_scaled4[, c("Country", "Life.Expectancy", "Unemployment", "Life.Expectancy_scaled", "Unemployment_scaled", "Region", "Income.Group")]

LE_ump <- na.omit(LE_ump)

# how many clusters
n_clusters <- 10

# initialize within sum of squares error
wss <- numeric(n_clusters)

# Set seed
set.seed(123)

for (i in 1:n_clusters) {
  # fit model
  km_LE_ump.out <- kmeans(LE_ump[, c("Life.Expectancy_scaled", "Unemployment_scaled")], centers = i)
  
  # save wss
  wss[i] <- km_LE_ump.out$tot.withinss
}

# create scree plot
wss_df <- tibble(clusters = 1:n_clusters, wss = wss)

scree_plot <- ggplot(wss_df, aes(x = clusters, y = wss, group = 1)) +
  geom_point() +
  geom_line() +
  scale_x_continuous(breaks = c(2, 4, 6, 8, 10)) +
  xlab('Number of clusters') +
  ylab('wss')

scree_plot

km_LE_ump.out <- kmeans(LE_ump[, c("Life.Expectancy_scaled", "Unemployment_scaled")], centers = 4)
km_LE_ump.out

# Plot results
LE_ump$cluster_id <- factor(km_LE_ump.out$cluster)
ggplot(LE_ump, aes(`Unemployment`, `Life.Expectancy`, color = cluster_id, label = `Country`, shape = `Income.Group`)) +
    geom_point(alpha = 0.5) +
    ggtitle("Cluster Analysis of Life Expectancy and Unemployment") +
    #geom_text(size = 3) +
    xlab("Unemployment") +
    ylab("Life Expectancy")
```
Cluster Analysis (6)
```{r}
# Life Expectancy and CO2
# Visualizing LE and CO2
ggplot(avg_data_by_country, aes(x = `CO2EmissionsperCapita`, y = `Life.Expectancy`, color = `Income.Group`)) +
  geom_point() +
  ggtitle("Avg Life Expectancy vs Avg CO2 Emissions per Capita") +
  xlab("CO2 Emissions") + ylab("Life Expectancy")

# Normalization
avg_data_by_country_scaled5 <- data.frame(avg_data_by_country)

avg_data_by_country_scaled5[, c("Life.Expectancy_scaled", "CO2EmissionsperCapita_scaled")] =  scale(avg_data_by_country[, c("Life.Expectancy", "CO2EmissionsperCapita")])

# Fitting and evaluating the model
# Get two columns of interest
LE_co2 <- avg_data_by_country_scaled5[, c("Country", "Life.Expectancy", "CO2EmissionsperCapita", "Life.Expectancy_scaled", "CO2EmissionsperCapita_scaled", "Region", "Income.Group")]

LE_co2 <- na.omit(LE_co2)

# how many clusters
n_clusters <- 10

# initialize within sum of squares error
wss <- numeric(n_clusters)

# Set seed
set.seed(123)

for (i in 1:n_clusters) {
  # fit model
  km_LE_co2.out <- kmeans(LE_co2[, c("Life.Expectancy_scaled", "CO2EmissionsperCapita_scaled")], centers = i)
  
  # save wss
  wss[i] <- km_LE_co2.out$tot.withinss
}

# create scree plot
wss_df <- tibble(clusters = 1:n_clusters, wss = wss)

scree_plot <- ggplot(wss_df, aes(x = clusters, y = wss, group = 1)) +
  geom_point() +
  geom_line() +
  scale_x_continuous(breaks = c(2, 4, 6, 8, 10)) +
  xlab('Number of clusters') +
  ylab('wss')

scree_plot

km_LE_co2.out <- kmeans(LE_co2[, c("Life.Expectancy_scaled", "CO2EmissionsperCapita_scaled")], centers = 4)
km_LE_co2.out

# Plot results
LE_co2$cluster_id <- factor(km_LE_co2.out$cluster)
ggplot(LE_co2, aes(`CO2EmissionsperCapita`, `Life.Expectancy`, color = cluster_id, label = `Country`, shape = `Income.Group`)) +
    geom_point(alpha = 0.5) +
    #geom_text(size = 3) +
    ggtitle("Cluster Analysis of Life Expectancy and CO2 Emissions per Capita") +
    xlab("CO2 Emissions per Capita") +
    ylab("Life Expectancy") +
  scale_x_log10()

```

Regression for all variables individually (Outliers)
```{r}
# Running linear regression of life expectancy against every variable in the dataset. 

# These were run just to get an idea of the individual effects of each of these variables. In the real world, LE is affected by a combination of variables. We will be doing multiple linear regression after this. 

# List of predictor variables in our data set. Grouping them like this in a list makes it easier to work with the variables.  

predictor_vars <- c("Prevalence.of.Undernourishment", "CO2.Emissions", "Health.Expenditure..", 
                    "Education.Expenditure..", "Unemployment", "Injuries", "Communicable.Diseases", 
                    "Non.Communicable.Diseases", "Access.to.clean.water", 
                    "GDPperCapita")


# Here we loop over each predictor variable to run a linear regression against Life Expectancy. Doing each regression individually would take up a lot of space so the loop does it efficiently. This way we will get a summary of each variable against Life Expectancy. 

for(var in predictor_vars) {
  formula_str <- paste("Life.Expectancy ~", var)
  model <- lm(formula_str, data = data)
  cat("------------------------------------------------\n")
  cat("Linear Regression Model for:", var, "\n")
  cat("------------------------------------------------\n")
  print(summary(model))
}


```

Regression Plot for Life Expectancy and GDP Per Capita (With Outliers)
```{r}

# Regression of LE and GDP Per Capita (Outliers)

# Run the regression model with outliers
gdp_and_le_with_outliers <- lm(Life.Expectancy ~ (GDPperCapita), data = data)

# Summary of the model to get coefficients, R-squared, and p-values
summary(gdp_and_le_with_outliers)

# Plot the data and the regression line
ggplot(data, aes(x = GDPperCapita, y = Life.Expectancy)) +
  geom_point() +  
  geom_smooth(method = "lm") +  
  ggtitle("Regression of Life Expectancy on GDP per capita with Outliers") +
  xlab("GDP (Billions)") +
  ylab("Life Expectancy")

```

Regression Plot fo Life Expectancy and Prevalence of Undernourishment (With Outliers)
```{r}

# Regression of LE and Prevalence of Undernourishment (Outliers)

# Run the regression model with outliers
undernourishment_and_le_with_outliers <- lm(Life.Expectancy ~ Prevalence.of.Undernourishment, data = data)

# Summary of the model to get coefficients, R-squared, and p-values
summary(undernourishment_and_le_with_outliers)

# Plot the data and the regression line
ggplot(data, aes(x = Prevalence.of.Undernourishment, y = Life.Expectancy)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ggtitle("Regression of Life Expectancy on Prevalence of Undernourishment with Outliers") +
  xlab("Prevalence of Undernourishment (%)") +
  ylab("Life Expectancy")


```

Regression for all variables individually (without Outliers)
```{r}

# List of our predictor variables that we want to run regressions for 
predictor_vars <- c("Prevalence.of.Undernourishment", "CO2.Emissions", "Health.Expenditure..", 
                    "Education.Expenditure..", "Unemployment", "Injuries", "Communicable.Diseases", 
                    "Non.Communicable.Diseases", "Access.to.clean.water", 
                    "GDPperCapita")

# Select just the columns you are interested in
data_subset <- data[, c("Life.Expectancy", predictor_vars)]

# Calculate Z-scores for the selected numeric columns
data_z <- as.data.frame(scale(data_subset[, predictor_vars]))

# Identify rows where any column's Z-score is greater than 3 or less than -3
outlier_rows <- apply(data_z, 1, function(row) any(abs(row) > 3))

#print(outlier_rows)

# Remove outliers from the subset
data_no_outliers <- data_subset[!outlier_rows, ]

#print(data_no_outliers)

# Loop over each predictor variable to run a linear regression against Life.Expectancy
for(var in predictor_vars) {
  formula_str <- paste("Life.Expectancy ~", var)
  model <- lm(formula_str, data = data_no_outliers)
  cat("------------------------------------------------\n")
  cat("Linear Regression Model for:", var, "\n")
  cat("------------------------------------------------\n")
  print(summary(model))
}


```

Regression Plot for Life Expectancy and Access to Clean Water (Without Outliers)
```{r}

# Run the regression model without outliers for Access to Clean Water
access_water_and_le_no_outliers <- lm(Life.Expectancy ~ Access.to.clean.water, data = data_no_outliers)

# Summary of the model to get coefficients, R-squared, and p-values
summary(access_water_and_le_no_outliers)

# Plot the data and the regression line
ggplot(data_no_outliers, aes(x = Access.to.clean.water, y = Life.Expectancy)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ggtitle("Regression of Life Expectancy on Access to Clean Water (Without Outliers)") +
  xlab("Access to Clean Water (%)") +
  ylab("Life Expectancy")


```

Regression Plot for Life Expectancy and Health Expenditure % (Without Outliers)
```{r}

# Run the regression model without outliers for Health Expenditure
health_exp_and_le_no_outliers <- lm(Life.Expectancy ~ Health.Expenditure.., data = data_no_outliers)

# Summary of the model to get coefficients, R-squared, and p-values
summary(health_exp_and_le_no_outliers)

# Plot the data and the regression line
ggplot(data_no_outliers, aes(x = Health.Expenditure.., y = Life.Expectancy)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ggtitle("Regression of Life Expectancy on Health Expenditure (Without Outliers)") +
  xlab("Health Expenditure (%)") +
  ylab("Life Expectancy")

```

Multivariate Regression (Outliers)
```{r}

# Loading the car libarary to be able to use the vif() function 
library(car)

# Run multivariate regression with outliers 
multivar_model_with_outliers <- lm(Life.Expectancy ~ Prevalence.of.Undernourishment + CO2.Emissions + Health.Expenditure.. + Education.Expenditure.. + Unemployment + Injuries + Communicable.Diseases + Non.Communicable.Diseases + Access.to.clean.water + GDPperCapita, data = data)

# Summary of the model without outliers
summary(multivar_model_with_outliers)

```

Multivariate Regression (without Outliers)
```{r}

library(car)

multivar_model_without_outliers <- lm(Life.Expectancy ~ Prevalence.of.Undernourishment + CO2.Emissions + Health.Expenditure.. + Education.Expenditure.. + Unemployment + Injuries + Communicable.Diseases + Non.Communicable.Diseases + Access.to.clean.water + GDPperCapita, data = data_no_outliers)

# Summary of the model without outliers
summary(multivar_model_without_outliers)

# Run vif function to check collinearity 
vif(multivar_model_with_outliers)

```

Multivariate Regression (without Outliers) - Non-Communicable and Injuries Variables removed 
```{r}

library(car)

multivar_model_without_outliers <- lm(Life.Expectancy ~ Prevalence.of.Undernourishment + CO2.Emissions + Health.Expenditure.. + Education.Expenditure.. + Unemployment + Communicable.Diseases + Access.to.clean.water + GDPperCapita, data = data_no_outliers)

# Summary of the model without outliers
summary(multivar_model_without_outliers)

# Run vif function 
vif(multivar_model_without_outliers)

```

